Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-06-23 literature/paper_draft.qmd
Update paper_draft.qmd
edit the abstract

# Notation

@@

# Abstract

[ This is pasted from the Project Description ]{style="color:red;"}

A collection of time series connected via a set of linear constraints is known as hierarchical time series. Forecasting these structures is challenging because the individual forecasts do not satisfy the linear constraints present in the data. To mitigate this issue, various forecast reconciliation approaches have been proposed in the literature, where the individual forecasts are adjusted by minimizing the mean squared reconciliation errors. Among these, the MinT (Minimum Trace) approach is widely used, and this method requires an estimate of the covariance matrix of the base forecast errors.

@@

In this project, we aim to assess the forecasting performance of MinT when different covariance estimators are used, and compare with the proposed estimators from published paper. with a primary focus on the NOVELIST (NOVEL Integration of the Sample and Thresholded Covariance) estimator, which shrinks the sample covariance toward its thresholded version. A thorough literature review will also identify other high-dimensional covariance estimators relevant to this project.

@@

    [ ... can include more estimators ... ]{style="color:red;"}

@@

<!-- Empirical findings to date   -->
<!-- Athanasopoulos et al. (2024) synthesise the accumulated evidence: MinT dominates single-level baselines in most studies; WLS or diagonal-shrinkage MinT is the current industry default; but gains plateau when off-diagonals are weak citeturn0file9.  Only a handful of papers explore richer covariance structures (e.g., block or factor shrinkage), and none benchmark them systematically against NOVELIST-type estimators. -->

>>>>

# Notation {-}

@@

# Abstract {-}

[This is pasted from the Project Description]{style="color:red;"}

A collection of time series connected via a set of linear constraints is known as hierarchical time series. Forecasting these series without respecting the hierarchical nature of the data can lead to incoherent forecasts across aggregation levels and lower accuracy. To mitigate this issue, various forecast reconciliation approaches have been proposed in the literature, where the individual forecasts are adjusted to satisfy the aggregation constraints. Among these, **MinT** (Minimum Trace) is widely used, however, it requires a good estimate of the covariance matrix of the base forecast errors.

@@

The current practice is to use the shrinkage estimator (often shrinking toward a diagonal matrix), but it lacks flexibility and might not fully utilise the prominent latent structure presented. In this project, we aim to assess the forecasting performance of MinT when different covariance estimators are used, namely NOVELIST (NOVEL Integration of the Sample and Thresholded Covariance), POET (Principal Orthogonal complEment Thresholding), and others.

@@

    [... can include more estimators ...]{style="color:red;"}

@@

<!-- Empirical findings to date   -->

<!-- Athanasopoulos et al. (2024) synthesise the accumulated evidence: MinT dominates single-level baselines in most studies; WLS or diagonal-shrinkage MinT is the current industry default; but gains plateau when off-diagonals are weak citeturn0file9.  Only a handful of papers explore richer covariance structures (e.g., block or factor shrinkage), and none benchmark them systematically against NOVELIST-type estimators. -->
